Search for Spatially Extended \fermi-LAT Sources Using Two Years of Data

### 2012-05-10 extended_catalog/paper/extended_search.tex
update

Because the two point-like source hypotheses has
three more parameters than the single extended source hypothesis (two spatial
parameters and two spectral parameters compared to one extension parameter),
we note that the $\tsext>\tsinc$ test is mathematically equivalent to testing that
\begin{equation}
  \aic_\text{ext} < \aic_\text{2pts} - 6.
\end{equation}
Therefore, our test has an 
equivalent Bayesian formulation requiring that $\aic_\text{ext}$ 
be sufficiently smaller than $\aic_\text{2pts}$.
}

>>>>

Because the two point-like source hypotheses has
three more parameters than the single extended source hypothesis (two spatial
parameters and two spectral parameters compared to one extension parameter),
we note that the $\tsext>\tsinc$ test is mathematically equivalent to testing that
\begin{equation}
  \aic_\text{ext} < \aic_\text{2pts} - 6.
\end{equation}
This equation requires that the extended source hypothesis be considerably preferred
over the hypothesis of two point-like sources.
Therefore, our original test is mathematically equivalent to one with a Bayesian interpretation.
